Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-03-25 manuscript/common_latex.tex
add lineage table explanation to common_latex

>>>>

\newcommand{\lineagetableexplanation}[3]%
[A two-sided t test was used to calculate p values.]{%
  Genes whose expression changed in #2 as compared to #3. #1 FDR
  is the False Discovery Rate as estimated by the Benjamini and
  Hochberg procedure \cite{Benjamini1995:bh_procedure}.
  $\mathrm{log}_2$ FC is the base-2 logarithm of the fold change from
  #2 to #3 .}

\newcommand{\lineagetableexplanationtypeiii}[2]{%
  \lineagetableexplanation[A nested type-III anova was used to
  calculate p values.]{#1}{#2}}
